### 2013-07-24 doc/asplos14/evaluation.tex
moved UPC data to text only, more pruning

\begin{table}[htb]
\begin{center}
\begin{tabular}{l|c|c|c|c}
         & \Grappa & XMT   & MPI  & UPC \\ \hline
GUPS     & 1       & 2.23  & 0.11 & -- \\ 
BFS      & 1       & 1.63  & 3.52 & -- \\ 
IntSort  & 1       & 3.59  & 5.36 & -- \\
UTS (T1) & 1       & 0.38  & --   & 0.09 \\ 
Pagerank & 1       & 4.35  & 4.87 & -- \\ 
\end{tabular}
\end{center}
\caption{Comparing \Grappa with XMT, optimized MPI and UPC. Numbers are presented as throughput on 64 nodes normalized to \Grappa.}
\label{tab:grappa-comparisons}
\end{table}

@@

The UPC UTS implementation includes an implementation of work-stealing
but has limited ability to overlap communication with
computation. Furthermore, it must execute heavyweight synchronization
operations when stealing. \Grappa benefits from its lightweight
context switching and support for fine-grained synchronization.

\paragraph{BFS.}
The Grappa and MPI BFS implementations are quite similar. They both
use the same graph representation, and they both depend on aggregation
for performance. The difference is that the BFS' aggregation is
integrated with the traversal code and specialized for the problem:
since the only messages required are edge traversals, the aggregation
buffers store only pairs of 8-byte vertex IDs.  In contrast, \Grappa
pays execution and space overhead in order to support aggregation of
arbitrary messages; the messages \Grappa aggregates include the two
8-byte vertex IDs along with 8 bytes of deserialization information as
well as 8 bytes of synchronization information. Furthermore, the MPI
implementation writes the edge information directly into the
aggregation buffer while \Grappa executes additional code to serialize
and deserialize the messages.

>>>>

\begin{table}[htb]
\begin{center}
\begin{tabular}{l|c|c|c}
         & \Grappa & XMT   & MPI   \\ \hline
GUPS     & 1       & 2.23  & 0.11 \\ 
BFS      & 1       & 1.63  & 3.52 \\ 
IntSort  & 1       & 3.59  & 5.36 \\
UTS (T1) & 1       & 0.38  & --   \\  % 0.09 for UPC
Pagerank & 1       & 4.35  & 4.87 \\ 
\end{tabular}
\end{center}
\caption{Comparing \Grappa with XMT and optimized MPI. Numbers are presented as throughput on 64 nodes normalized to \Grappa.}
\label{tab:grappa-comparisons}
\end{table}

@@

We also compare with an UPC UTS implementation, which is nearly 10$\times$
\emph{slower} than \Grappa. Our UPC version supports work-stealing but has
limited ability to overlap communication with computation. Also, it
employs heavyweight synchronization operations when stealing. \Grappa
benefits from its lightweight context switching and support for fine-grained
synchronization.

\paragraph{BFS.}
The \Grappa and MPI BFS implementations are quite similar. They both
use the same graph representation, and they both depend on aggregation
for performance. The difference is that the BFS' aggregation is
integrated with the traversal code and specialized for the problem:
since the only messages required are edge traversals, the aggregation
buffers store only pairs of 8-byte vertex IDs.  In contrast, \Grappa
pays execution and space overhead in order to support aggregation of
arbitrary messages; the messages \Grappa aggregates include the two
8-byte vertex IDs along with 8 bytes of deserialization information as
well as 8 bytes of synchronization information. Furthermore, the MPI
implementation writes the edge information directly into the
aggregation buffer while \Grappa executes additional code to serialize
and deserialize the messages.
